Energy and the CES production function

### 2015-09-23 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Corrected line types for historical data graph.

  # Make (and return) the graph
  ggplot() +
    geom_line(data=fittedGraphData, mapping=aes(x=Year, y=value, group=label, linetype=label)) +
    scale_linetype_manual(values=c(1,2,4,3), name="") +
    facet_grid(flavor ~ Country) +
    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
    scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
    xlab("") +
    ylab("Indexed GDP (1960=1)") +
    xy_theme()
}
@

@@

<<Graphs_CESkle_resample_alphas, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Resample output elasticities for CES models with $(kl$)$e$ nesting.">>=
ReModels %>% 
  gather(factor, elasticity, oe1, oe2, oe3) %>%
  ggplot(aes(x=Year)) + 
  geom_line( 
    aes(y = elasticity,
        alpha = grepl("orig", id),
        group = interaction(id, factor),
        color = factor,
        linetype = factor,
        size = grepl("orig", id)
    ) ) +
  facet_grid(. ~ Country) +
  scale_alpha_manual(
    name = "",
    values = c(.3, 1),
    guide = FALSE
  ) + 
  scale_color_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c("black", "black", "gray70"),
    guide=FALSE
  ) +
  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
  scale_size_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values = c(.3, .9),
    guide = FALSE) +
  scale_linetype_manual( 
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c(2,3,1) ) + 
  xy_theme() +
  labs(x="", y="")
@

@@

<<resample_graph_alpha, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
                labels=c("alpha[k]", "alpha[l]", "alpha[e]"), size=2.0)
@

>>>>

  ggplot() +
    geom_line(data=fittedGraphData, mapping=aes(x=Year, y=value, group=label, linetype=label, size=label)) +
    scale_linetype_manual(values=c(1,2,4,3), name="") +
    scale_size_manual(name = "", values=c(1, 0.5, 0.5, 0.5)) +
    facet_grid(flavor ~ Country) +
    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
    scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
    xlab("") +
    ylab("Indexed GDP (1960=1)") +
    xy_theme()
}
@

@@

<<resample_graph_alpha, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Resample output elasticities for CES models with $(kl$)$e$ nesting.">>=
ReModels %>% 
  gather(factor, elasticity, oe1, oe2, oe3) %>%
  ggplot(aes(x=Year)) + 
  geom_line( 
    aes(y = elasticity,
        alpha = grepl("orig", id),
        group = interaction(id, factor),
        color = factor,
        linetype = factor,
        size = grepl("orig", id)
    ) ) +
  facet_grid(. ~ Country) +
  scale_alpha_manual(
    name = "",
    values = c(.3, 1),
    guide = FALSE
  ) + 
  scale_color_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c("black", "black", "gray70"),
    guide=FALSE
  ) +
  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
  scale_size_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values = c(.3, .9),
    guide = FALSE) +
  scale_linetype_manual( 
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c(2,3,1) ) + 
  xy_theme() +
  labs(x="", y="")
@

@@

<<resample_graph_alpha_ternary, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
                labels=c("alpha[k]", "alpha[l]", "alpha[e]"), size=2.0)
@
